### 2024-03-27 tesis_Ashish/Chapter4/chapter4.tex
update 28 Mar

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/SS1_SS2_bkg_pcc_1.png}
\caption[Background estimation]{2D histogram filled with the Avg. PCC rate evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
\label{fig:sigmavis_ss_backg}
\end{figure}

@@

\newpage
\item Afterglow: Systematic uncertainty due to afterglow background is determined by calculating the mean of the type 1 and type 2 afterglow residuals that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.

>>>>

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/SS1_SS2_bkg_pcc_1.png}
\caption[Background estimation]{2D histogram filled with the Avg. PCC evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
\label{fig:sigmavis_ss_backg}
\end{figure}

@@

\newpage
\item Afterglow: Systematic uncertainty due to afterglow background is determined by calculating the mean of the type 1 and type 2 afterglow residuals. Type 1 afterglow residuals are determined by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch. Type 2 afterglow residuals focus on the luminosity of the second  empty bunches after a colliding bunch, compared to the luminosity of the colliding bunch itself.
  %that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
